Chemically Selective Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-05-07 Ben_Manuscripts/transport/Draft.tex
Beginnings of intro outline

  Cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
  membranes are nanostructured membranes that may be able to achieve the
  selectivity of RO membranes while maintaining the high permeability
  of NF membranes.~\cite{zhou_supported_2005} The H\textsubscript{II}
  phase is formed when LLC monomers self-assemble into hexagonally packed
  and uniform-sized pores.~\cite{smith_ordered_1997} Alignment and subsequent
  cross-linking of the hexagonal mesophases yields a mechanically strong
  membrane.~\cite{feng_scalable_2014,feng_thin_2016} The uniform-sized pores
  enforce a strict molecular-size cut-off while the hexagonal geometry is 
  ideal for high permeability.~\cite{zhou_supported_2005} Additionally, 
  because the LLC monomers are salts, Donnan exclusion plays a role in 
  rejection of charged molecules upon pore entry.~\cite{donnan_theory_1995}

  Under the right conditions, amphiphilic molecules can self-assemble
  into ordered nanostructures that may be capable of performing highly selective separations.
  \begin{itemize}
    \item Uniform-sized pores characteristic of these systems enforce a 
    molecular-size cut-off, eliminating issues related to the polydisperity 
    of NF pores.
    \item By controlling the chemical identity of moeties inside the pores, 
    it may be possible to tune these types of materials for solute-specific
    separations.
  \end{itemize}

  Lyotropic liquid crystals (LLCs) are known to form the type I bicontinuous
  (Q\textsubscript{I}) and inverted hexagonal (H\textsubscript{II}) phases.
  \begin{itemize}
	\item When cross-linked, these materials can function as separations
	 membranes.
	\item The H\textsubscript{II}
  \end{itemize}

@@

  In addition to geometric factors which make H\textsubscript{II} membranes
  ideal for selective separations, they have the potential to further disrupt
  conventional membrane separation techniques by being selective based not
  only on solute size and charge, but on chemical functionality as well. 
  The functional LLC monomer head groups that occupy the pore region of the
  membrane can interact with solutes. Dischinger et al.~studied the 
  performance of a Q\textsubscript{I} phase LLC membrane, which has a 
  similar pore topology to the H\textsubscript{II} phase, but a more 
  tortuous geometry, and observed a range of selectivities dependent on the
  anion coordinated to the LLC monomer.~\cite{dischinger_effect_2017} Intelligent 
  design of LLC monomers have the potential to help us tailor membranes for 
  solute-specific separations.

  While H\textsubscript{II} membranes have been synthesized and characterized
  in a lab setting, there is a limit to the level of detail that can be obtained 
  from experiment. These membranes have been primarily characterized with 
  size-exclusion experiments which can give an estimate of pore size as well as
  selectivity based on differences in solute sizes~\cite{zhou_supported_2005}. 
  However, size exclusion does not appear to be sufficient to fully describe LLC
  membranes. Dischinger et al. studied a similar membrane and found that they do
  not separate purely on the basis of size.~\cite{dischinger_effect_2017} Empirical modeling revealed correlations
  between various solute physicochemical properties and observed solute rejection. 
  Although there was some agreement with their empirical model, it does not
  offer a sufficiently detailed explanation of governing molecular interactions.~\cite{dischinger_effect_2017}
%============= 
%  The separation performance of these membranes has been 
%  primarily characterized with size-exclusion experiments which emphasizes 
%  selectivity based on the ability to enter a given pore.~\cite{zhou_supported_2005}
%  %MRS4: might confuse readers here - talking about both size exclusion as a method to characterize the membranes, and 
%  %separation BY size exclusion; maybe rephrase?
%  %BJC4: Hmm, by characterization, I mean testing their ability to separate, so I'm 
%  While size-exclusion is a useful separation, it 
%  cannot reliably purify a solution where the solute size is on the same order as water. Therefore, it is
%  important to take advantage of material properties other than pore size. 
%  Unfortunately, this is a more complicated design problem. Experimental transport
%  studies of small solutes in a Q\textsubscript{I} phase membrane yielded 
%  unclear trends due to interactions between solutes and pore moieties. Although
%  the authors identified some correlation between select physicochemical properties
%  and solute transport trends, their empirical model does not offer a sufficient 
%  explanation of the molecular interactions responsible for those correlations~\cite{dischinger_effect_2017}
  %MRS4: expand the above.  What was discovered, and why was it unfortunate to the thesis?  
  % I though it actually helped the thesis here since there was something happening that WASN'T just size dependence?

>>>>

%  Cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
%  membranes are nanostructured membranes that may be able to achieve the
%  selectivity of RO membranes while maintaining the high permeability
%  of NF membranes.~\cite{zhou_supported_2005} The H\textsubscript{II}
%  phase is formed when LLC monomers self-assemble into hexagonally packed
%  and uniform-sized pores.~\cite{smith_ordered_1997} Alignment and subsequent
%  cross-linking of the hexagonal mesophases yields a mechanically strong
%  membrane.~\cite{feng_scalable_2014,feng_thin_2016} The uniform-sized pores
%  enforce a strict molecular-size cut-off while the hexagonal geometry is 
%  ideal for high permeability.~\cite{zhou_supported_2005} Additionally, 
%  because the LLC monomers are salts, Donnan exclusion plays a role in 
%  rejection of charged molecules upon pore entry.~\cite{donnan_theory_1995}

  Under the right conditions, amphiphilic molecules can self-assemble
  into ordered nanostructures that may be capable of performing highly
  selective separations.
  \begin{itemize}
    \item The uniform-sized aqueous pores characteristic of these types of
    systems enforce a molecular-size cut-off, eliminating issues related to the
    polydisperity of NF pores.
    \item By controlling the chemical identity of moeties inside the pores, 
    it may be possible to tune these types of materials for solute-specific
    separations.
  \end{itemize}

  Amphiphilic lyotropic liquid crystals (LLCs) are known to form the type I 
  bicontinuous (Q\textsubscript{I}) and inverted hexagonal (H\textsubscript{II})
  phases.
  \begin{itemize}
	\item When cross-linked, these materials can function as separations
	 membranes.
	\item The H\textsubscript{II} phase has hexagonally packed, straight
	pores which is the ideal geometry for high throughtput separations.
	\item However, the synthesis of H\textsubscript{II} membranes with 
	highly aligned hexagonal mesophases has been a challenge that has 
	prevented this type of membrane's viability.
	\item The Q\textsubscript{I} has been studied with much more 
	success. 
  \end{itemize}

@@

%  In addition to geometric factors which make H\textsubscript{II} membranes
%  ideal for selective separations, they have the potential to further disrupt
%  conventional membrane separation techniques by being selective based not
%  only on solute size and charge, but on chemical functionality as well. 
%  The functional LLC monomer head groups that occupy the pore region of the
%  membrane can interact with solutes. Dischinger et al.~studied the 
%  performance of a Q\textsubscript{I} phase LLC membrane, which has a 
%  similar pore topology to the H\textsubscript{II} phase, but a more 
%  tortuous geometry, and observed a range of selectivities dependent on the
%  anion coordinated to the LLC monomer.~\cite{dischinger_effect_2017} Intelligent 
%  design of LLC monomers have the potential to help us tailor membranes for 
%  solute-specific separations.

%  While H\textsubscript{II} membranes have been synthesized and characterized
%  in a lab setting, there is a limit to the level of detail that can be obtained 
%  from experiment. These membranes have been primarily characterized with 
%  size-exclusion experiments which can give an estimate of pore size as well as
%  selectivity based on differences in solute sizes~\cite{zhou_supported_2005}. 
%  However, size exclusion does not appear to be sufficient to fully describe LLC
%  membranes. Dischinger et al. studied a similar membrane and found that they do
%  not separate purely on the basis of size.~\cite{dischinger_effect_2017} Empirical modeling revealed correlations
%  between various solute physicochemical properties and observed solute rejection. 
%  Although there was some agreement with their empirical model, it does not
%  offer a sufficiently detailed explanation of governing molecular interactions.~\cite{dischinger_effect_2017}
%============= 
%  The separation performance of these membranes has been 
%  primarily characterized with size-exclusion experiments which emphasizes 
%  selectivity based on the ability to enter a given pore.~\cite{zhou_supported_2005}
%  %MRS4: might confuse readers here - talking about both size exclusion as a method to characterize the membranes, and 
%  %separation BY size exclusion; maybe rephrase?
%  %BJC4: Hmm, by characterization, I mean testing their ability to separate, so I'm 
%  While size-exclusion is a useful separation, it 
%  cannot reliably purify a solution where the solute size is on the same order as water. Therefore, it is
%  important to take advantage of material properties other than pore size. 
%  Unfortunately, this is a more complicated design problem. Experimental transport
%  studies of small solutes in a Q\textsubscript{I} phase membrane yielded 
%  unclear trends due to interactions between solutes and pore moieties. Although
%  the authors identified some correlation between select physicochemical properties
%  and solute transport trends, their empirical model does not offer a sufficient 
%  explanation of the molecular interactions responsible for those correlations~\cite{dischinger_effect_2017}
  %MRS4: expand the above.  What was discovered, and why was it unfortunate to the thesis?  
  % I though it actually helped the thesis here since there was something happening that WASN'T just size dependence?
